Self Referencing Sequences

### 2014-11-05 draft.tex
added another poem

\noindent For the final draft,\\
we will improve the haikus\\
(and the whole paper).
\end{document}

>>>>

\noindent For the final draft,\\
we will improve the haikus\\
(and the whole paper).

\subsection{Poem}

\noindent A sequence refering to its past\\
warrants many questions to be asked.\\
These sequences are deterministic \\
and their read distances an imporant statistic.
\\

\noindent We want to compute the limiting density\\
so we've defined a process.\\
But one would be a fool to not follow our rule.\\
And compute the density for 1, 3.\\

\noindent The big question remains unanswered.\\
The density of 1,2 which seems to be one half.\\
Our rules are for numbers of a certain class.\\
Unfortunetly, dealing with 1,2 is a pain in the a**.\\

\end{document}
